\LARGE \bf Geometric Adaptive Control of Attitude Dynamics on $\SO$\\ with State Inequality Constraints

### 2015-09-22 ACC16.2.tex
starting adaptive control law section

\subsection{Adaptive Control}

\begin{enumerate}[(i)]
	\item An upper bound of \( \norm{e_{R_B}} \) is given as:
	\begin{align}
		\norm{e_{R_B}} \leq \frac{\sin{\frac{\pi}{2} - \theta}}{\alpha \parenth{\beta - \cos \theta}}
	\end{align}
\end{enumerate}
Add the disturbance term and introduce adaptive update law

@@

Get three polynomials (can use cubic or quartic functions to get analytical result)

Define domain of consideration \( \Psi \leq \psi \) and \( r^T R^T v \leq \beta \)

@@

Improves upon previous work by extending to the full nonlinear manifold representation and avoids quaternion ambiguities

>>>>

\subsection{Adaptive Control}
We extend the results of the previous section with the addition of a fixed but unknown disturbance \( \Delta \).
This scenario is typical of many mechanical systems and represents unmodeled dynamics or external moments acting on the system.
For example, Earth orbiting spacecraft typically experience both a torque due to a gravitational gradient as well as external torques to due solar radiation pressure.
Aerial vehicles will similarly experience external torques due to air currents or turbulence.
A smooth control system is introduced to asymptotically stabilize the system to a desired attitude while ensuring that state constraints are satisfied.

\begin{prop}[Bound on \( \dot{e}_R \)]\label{prop:eR_dot_bound}
Consider a domain \( D \) about the desired attitude defined as
\begin{align}
	D = \braces{R \in \SO \vert \Psi < \psi < h1, r^T R^T v < \beta < \cos \theta} \, . \label{eqn:domain}
\end{align}
An upper bound of \( \dot{e_R} \) is given by

equation for H

list the bounds on each of the terms

Proof of the derivation of them

Lyapunov analysis which shows that it's stable

Adaptive update law and control input

\begin{enumerate}[(i)]
	\item An upper bound of \( \norm{e_{R_B}} \) is given as:
	\begin{align}
		\norm{e_{R_B}} \leq \frac{\sin{\frac{\pi}{2} - \theta}}{\alpha \parenth{\beta - \cos \theta}}
	\end{align}
\end{enumerate}
\end{prop}
Add the disturbance term and introduce adaptive update law

@@

@@

Improves upon previous work by extending to the full nonlinear manifold representation and avoids quaternion ambiguities/singularities
